Supplemental Material: Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling.

### 2020-01-28 Ben_Manuscripts/stochastic_transport/cover_letter.tex
update letter.
New figures and small edits
Tweaked formatting.

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and
	Michael R.  Shirts, for consideration for publication as a Research
	Article in Physical Review E. We expect this work to be of significant
	interest to researchers who study complex dynamics in both structured
	and amorphous soft materials. \\

	In this article, we use 5$\mu$s molecular dynamics (MD) simulations of
	solutes moving through the pores of an inverted hexagonal phase
	lyotropic liquid crystal (LLC) polymer membrane in order to
	parameterize two different stochastic time series models capable of
	predicting solute flux and selectivity on a macroscopic scale.
	Realizations of both models quantitatively reproduce the mean squared
	displacements (MSDs) exhibited by the solutes in our MD simulations. We then
	demonstrate how we can use realizations orders of magnitude longer than
	our MD simulations in order to predict solute flux and selectivity.
	This is among the first studies to apply time series modeling
	approaches in order to predict bulk materials properties. \\

@@

	%BJC: included phone numbers because it asked to do so in author's guide.
	\noindent Some suggestions for reviewers are:
	\begin{enumerate}

		\item Ralf Metzler is an expert in anomalous diffusion theory
			with applications to soft materials. (University of
			Potsdam, \href{mailto:kakania@uni-potsdam.de}{kakania @
			uni-potsdam.de})

@@

		\item Richard Lueptow uses molecular simulations to understand
			transport processes in polymeric nanofiltration and
			reverse osmosis membranes. (Northwestern University
			\href{mailto:r-lueptow@northwestern.edu}{r-lueptow@northwestern.edu})

>>>>

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and
	Michael R.  Shirts, for consideration for publication as a Research
	Article in Physical Review E. We expect this work to be of significant
	interest to researchers who study complex dynamics in both structured
	and amorphous soft materials.

	In this article, we use 5$\mu$s molecular dynamics (MD) simulations of
	solutes moving through the pores of an inverted hexagonal phase lyotropic
	liquid crystal (LLC) polymer membrane in order to parameterize two different
	stochastic time series models capable of predicting solute flux and selectivity
	on a macroscopic scale.  Realizations of both models quantitatively reproduce
	the mean squared displacements (MSDs) exhibited by the solutes in our MD
	simulations. We then demonstrate how we can use realizations orders of
	magnitude longer than our MD simulations in order to predict solute flux and
	selectivity.  This is among the first studies to apply time series modeling
	approaches in order to predict macroscopic transport properties from molecular
	dynamics trajectories.

@@

	\noindent Some suggestions for reviewers are:
	\begin{enumerate}

		\item Ralf Metzler is an expert in anomalous diffusion theory
			with applications to soft materials. (University of
			Potsdam, \href{mailto:kakania@uni-potsdam.de}{kakania@uni-potsdam.de})

@@

		\item Richard Lueptow uses molecular simulations to understand
			transport processes in polymeric nanofiltration and
			reverse osmosis membranes. (Northwestern University,
			\href{mailto:r-lueptow@northwestern.edu}{r-lueptow@northwestern.edu})
